Data Imputation as a Query Optimization

### 2016-12-07 paper/introduction.tex
paper: clean up in intro and relatedwork

In this paper, we present \ProjectName, a database system which is designed to interact with a dirty dataset as though it were clean.
The guiding design principle of \ProjectName is that the user should never see missing data or have to modify their queries to account for it.
To achieve this goal, we perform imputation on the fly, during query execution.
We find that performing imputation during query execution allows our system to flexibly trade accuracy for computation time.

>>>>

In this paper, we present \ProjectName{}, a database system which is designed to interact with a dirty dataset as though it were clean.
The guiding design principle of \ProjectName{} is that the user should never see missing data or have to modify their queries to account for it.
To achieve this goal, we perform imputation on the fly, during query execution.
We find that performing imputation during query execution allows our system to flexibly trade accuracy for computation time.

### 2016-12-07 paper/relatedwork.tex
paper: clean up in intro and relatedwork

\subsection{Missing Values and Databases}
There is a long history in the database community surrounding the
treatment of nulls. As early as 1973, \cite{codd1973understanding}
provides a treatment of the semantics of null. Multiple
papers have described various (at times conflicting) treatments
of nulls \cite{grant1977null}. \ProjectName's main design invariant - that no relational operator
see attributes with missing values for attributes it must operate on - eliminates
the need to handle null value semantics, while guaranteeing soundness (modulo
imputation strategy) of the query evaluation.

>>>>

\subsection{Missing Values and Databases}
There is a long history in the database community surrounding the
treatment of nulls. As early as 1973, \cite{codd1973understanding}
provides a treatment of the semantics of null. Multiple
papers have described various (at times conflicting) treatments
of nulls \cite{grant1977null}. \ProjectName's main design invariant - that no relational operator
see attributes with missing values for attributes it must operate on and users should never see
missing data - eliminates
the need to handle null value semantics, while guaranteeing soundness (modulo
imputation strategy) of the query evaluation.
